\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-05-25 paper/paper.tex
CHanged data section

\begin{figure}[H]
\includegraphics[width=\textwidth]{fig/data_sum.pdf}
\caption{Left: Total number of failures (log scale) for each of the drive-models in the Backblaze data. Right: Total time in operation (log scale) for each of the drive-models in the Backblaze data.  Both plots are sorted based on the total number of failures.}
\label{fig1}
\end{figure}

Probability plotting is an effective method to check the adequacy of various parametric models to the data.  Identifying whether failure data follows a specific distribution is difficult to do by eye: especially when looking at pdfs or other non-linear plots.  However, if we can linearize the cumulative distribution function it is easier to visually assess a distributional goodness of fit; if a model is appropriate, a non parametric estimate of $\hat{F(t)}$ graphed on linarized probability scales should approximately follow a straight line. \\

For the hard drive data we first estimate the empirical cdf for each model using the Kaplan-Meier estimator (KME)\cite{kaplan}.  With left truncation, however, the KME, which we denote by $\widehat{F(t)_{KM}}$, is conditional based on hard drive $i$ surviving up to time $\tau_i^L$ where $L$ is the amount of time the hard drive was running before Backblaze starting monitoring the drive.  To correct the non-parametric estimates, we adapt the adjustment method outlined by Turnbull, and given in more detail by Meeker and Escobar \cite{turnbull,meeker}.  For each hard drive model we select $t_{d,\text{min}}^L$, the smallest left truncated time in the sample.  Since $Pr(T>t_{d,\text{min}}^L)$, the probability a hard drive has survived up to $t_{d,\text{min}}^L$, is a function of the model parameters, by sampling from the full posterior distribution we can easily compute its posterior median, $\widehat{Pr_(T>t_{d,\text{min}}^L)}$. We use this to shift and rescale the KM thus  the unconditional distribution of time to failure, as in

$$\widehat{F(t)_{KMadj}} = .$$

@@

Finally, the lower right panel, corresponding to Model 4, shows that, by allowing $\pi_d$ to vary by drive model, there is greater variability in the early rate of failure and, for some drive models, the forecasted fraction failing is adjusted downward. 
\\
Comment: I think I prefer to use points for Kaplan Meier.  Using the connected dots almost makes it look like another model fit, rather than the actual observed failure data.  What do you think? \\

\begin{figure}[H]
    \centering
   \includegraphics[width=5.0in]{fig/brand_compare_nobands.pdf}
		\caption{Estimated GFLP for all 4 Model Specifications.  Truncated Adjusted Kaplan Meier points are also presented.    \label{fig:first}} 
\end{figure}

>>>>

\begin{figure}[H]
\includegraphics[width=\textwidth]{fig/data_sum.pdf}
\caption{Left: Total number of failures (log scale) for each of the drive-models in the Backblaze data. Right: Total time in operation (log scale) for each of the drive-models in the Backblaze data.  Both plots are sorted based on the total number of failures.}
\label{fig2}
\end{figure}

Probability plotting is a simple method to assess the adequacy of (log)location-scale families of probability models to the data.  Identifying whether failure data are consistent with a specific family of distributions is difficult to do by examining a histogram or other density estimate. By transform the y-axis of the estimated cumulative distribution function (cdf), denoted by $\widehat{F(t)}$, by the inverse cdf of for the standardized distribution, a visual comparison of the plot to a straight line can be an effective informal test for distributional goodness of fit.

Applying this method to the hard drive data, we first must estimate the empirical cdf for each model using the Kaplan-Meier estimator \cite{kaplan}.  With left truncation, however, the standard Kaplan-Meier estimator for drive-model $d$, denoted by $\widehat{F_d(t)}_{KM}$, is conditional on survival up to $t_{d,\text{min}}^L$, the shortest reported running time of all units of drive-model $d$ for which records are available. To produce unconditional estimates, we adapt the adjustment method outlined by Turnbull, and given in more detail by Meeker and Escobar \cite{turnbull,meeker}.  For each hard drive model we select $t_{d,\text{min}}^L$, the smallest left truncated time in the sample.  By sampling from the full posterior distribution, since $Pr(T>t_{d,\text{min}}^L|\theta_d)$ (the probability a hard drive has survived up to $t_{d,\text{min}}^L$) is a function of the model parameters, we can easily compute its posterior median, $\widehat{A}_{\text{med}} = \widehat{Pr}_(T>t_{d,\text{min}}^L|\theta_d)$. We compute the adjusted estimate by

$$\widehat{F(t)}_{KMadj} = \widehat{A}_{\text{med}} + \left(1 - \widehat{A}_{\text{med}}\right)\widehat{F_d(t)}_{KM},\; t>t_{d,\text{min}}^L.$$

While this adjustment is negligible for the majority of drive-models, five drive-models receive upward adjustments of greater than 5 percent and the estimated time to failure distribution of one drive-model (30) was adjusted by nearly 16 percent, in part because the shortest truncation time for all observed units was approx. 2.3 years.

@@

Finally, the lower right panel, corresponding to Model 4, shows that, by allowing $\pi_d$ to vary by drive model, there is greater variability in the early rate of failure and, for some drive models, the forecasted fraction failing is adjusted downward. 
First look at the overlaid posterior credible bands.  Perhaps pick 4 different drive models and present a plot like the figure below.  Bands are for full model, and the solid line is the full model fit. \\

\begin{figure}[H]
    \centering
   \includegraphics[width=5.0in]{fig/mod40_bands.pdf}
		\caption{Drive Model 40 \label{fig:first}} 
\end{figure}
